Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-12 journal paper/content/related_work.tex
More edits.

\subsection{Background: the three classes of algorithms [IN PROGRESS, don't read]}
\label{sec:related-classes}

@@

We are concerned with the following problem. There are $T$ rounds and $K$ \emph{arms} to choose from. In each round $t\in [T]$, the algorithm chooses an arm and receives a reward $r_t\in[0,1]$ for this arm, drawn from a fixed but unknown distribution. Algorithm's goal is to maximize the total reward. A standard performance measure is \emph{regret}, defined as the difference in the total expected reward between the algorithm and the best fixed arm.%
\footnote{In a formula, regret is
    $\E\sbr{ T\cdot \max_{\text{arms $a$}}\mu_a -  \sum_{t\in[T]} r_t }$,
where $\mu_a$ is the mean reward of arm $a$.}
The primary concern is the asymptotic growth rate of regret as a function of $T$.

@@

@@

Switching from ``greedy" to ``exploration-separating" to ``adaptive-exploration" algorithms involves substantial adoption costs in infrastructure and personnel training.

>>>>

\subsection{Background for non-specialists: the three classes of algorithms [IN PROGRESS]}
\label{sec:related-classes}

@@

\xhdr{Fundamentals.}
We are concerned with the following problem. There are $T$ rounds and $K$ \emph{arms} to choose from. In each round $t\in [T]$, the algorithm chooses an arm and receives a reward $r_t\in[0,1]$ for this arm, drawn from a fixed but unknown distribution. Algorithm's goal is to maximize the total reward.

A standard performance measure is \emph{regret}, defined as the difference in the total expected reward between the algorithm and the best arm.%
\footnote{In a formula, regret is
    $T\cdot \max_{\text{arms $a$}}\mu_a 
    -  \E\sbr{ \sum_{t\in[T]} r_t }$,
where $\mu_a$ is the mean reward of arm $a$.}
Since regret is normalized by the best arm, it allows to compare algorithms across different problem instances. 
The primary concern is the asymptotic growth rate of regret as a function of the time horizon $T$.

@@

\xhdr{Advanced aspects.}
Switching from ``greedy" to ``exploration-separating" to ``adaptive-exploration" algorithms involves substantial adoption costs in infrastructure and personnel training \citep{DS-arxiv}.

@@

%\xhdr{}
